---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)

```

NYC Restaurant Inspection Data set possible questions/analyses:

* Does restaurant grade distribution vary across boroughs? 

* How do restaurant grade/inspections vary across types of restaurants? 

* What types of violations are most/least common? (how does this vary across grades?)


```{r loading and cleaning }
nyc_restaurant_inspections <- read_csv("../data_hw6/DOHMH_New_York_City_Restaurant_Inspection_Results.csv", col_names = TRUE) %>% 
  rename(restaurant_id = camis, restaurant_name = dba) %>% 
  filter(is.na(grade) == FALSE)
```

Your dashboard should include at least three distinct plot types (e.g. scatterplots, line plots, bar plots, box plots, etc.).



Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
# put plotly code in these code chunks to specify the dashboard orientation/plots

nyc_restaurant_inspections %>% 
  filter(grade %in% c("A", "B", "C")) %>%
  select(cuisine_description, grade) %>%
  group_by(cuisine_description) %>%
  count(grade) %>%
  spread(key = grade, value = n) %>%
  plot_ly(x = ~cuisine_description, y = ~A, type = 'bar', name = 'A') %>%
  add_trace(y = ~B, name = 'B') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack') %>%
  add_trace(y = ~C, name = 'C') %>%
  layout(yaxis = list(title = 'Count'), barmode = 'stack')





  
  




```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

